|

### 2023-05-19 manuscript/paper.Rmd
updates.

---
title: |
  |  \Large Eras in baseball: Change-Ups and Change Points: An Exploration of Baseball's Historic Eras
author: | 
  | \large Mena Whalen \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Center for Data Science and Consulting \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`mwhalen3@luc.edu`](mailto:mwhalen3@luc.edu) \vspace{-1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Center for Data Science and Consulting \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1mm}
abstract: |
  | Baseball is some weird and wild shit. \vspace{2mm}
  | *Keywords*: change point analysis, baseball, 
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

>>>>

---
title: |
  |  \Large Eras in baseball: Change-Ups and Change Points: An Exploration of Baseball's Historic Eras
author: | 
  | \large Mena Whalen \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Center for Data Science and Consulting \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`mwhalen3@luc.edu`](mailto:mwhalen3@luc.edu) \vspace{-1mm}
  |
  | \large Brian M. Mills \vspace{-1.1mm}
  | \normalsize College of Education \vspace{-1mm}
  | \normalsize University of Texas at Austin \vspace{-1mm}
  | \normalsize Austin, TX 60660 \vspace{-1mm}
  | \normalsize [`brian.mills@austin.utexas.edu`](mailto:brian.mills@austin.utexas.edu) \vspace{-1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Center for Data Science and Consulting \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1mm}
abstract: |
  | Baseball is some weird and wild shit. \vspace{2mm}
  | *Keywords*: change point analysis, baseball, 
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---
